State of the art in {\ttlit Sentiment Analysis}

### 2014-11-12 paper/chapters/1_introduction.tex
add introduction

try to cite someone \autocite{Kouloumpis2011}

>>>>

Within the last years Twitter and similar social media platforms grew considerably in terms of user numbers and mainstream fame. Twitter has about 284 Mio. active users, generating approximately 500 Mio. posts\footnote{posts are also known as tweets} on a single day\footnote{\url{https://about.twitter.com/company}, Effective 12.11.2014}. These impressive numbers show the amout of information generated by the crowd. Furthermore Twitter is able to reach a vast number of potential customers especially for consumer businesses. As a result the named services gain more and more acceptance as opinion platforms and powerful tools for both, opinion leader as well as pollister. This trend influenced various marketing and sales strategies and created a new market for companies specialiced on sentiment analysis of tweets, like tweetfeel\footnote{\url{www.tweetfeel.com}}, Social Mention\footnote{\url{www.socialmention.com}} and Twitratr\footnote{\url{www.twitratr.com}}.

% whats sentiment analysiss
The aim of sentiment analysis is to determine and try to measure positive and negative feelings, emotions and opinions written in a text. English as language allows to express the same intent in different ways. The main challenge therefore consists in abstracting the intention of the writer from the grammatic and language specific rules.

% steps
In general sentiment analysis can be splitted into 2 steps: a preprocessing and a constitutive sentiment analysis phase. In Twitter sentiment analysis there is another step right bevor preprocessing: fetching the data from the application programming interface (API). This task is not trivial, because the official API is limited regarding the datasets fetched within certain intervals. This leads to the requirement of a caching mechanism to avoid fetching the same tweets multiple times and allow the usage of more datasets.

\begin{tikzpicture}[auto, node distance=3.3cm,>=latex']
    \node [block] (input) {Twitter};
    \node [block, right of=input, pin={[pinstyle]above:Cache}] (proprocess) {Preprocessing};
    \node [block, right of=proprocess] (analyse) {Analysis};

    \draw [->] (proprocess) -- node[name=u] {$u$} (analyse);
    \draw [->] (input) -- node {$fetch$} (proprocess);
\end{tikzpicture}

% a lot research on how sentiment is sentiment is expressed in other media types social quite new
While sentiment analysis of conventinal ressources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively new. Excpecially the possibility of priorizing keywords\footnote{known as hashtags} and the common usage of emoticons lead to advanced possibilities to categorize feelings of posts.

% perfekt für marktforschung und meinungsbildung

### 2014-11-12 paper/paper.tex
Paper: Started chapter Preprocessing
add introduction

\documentclass{sig-alternate}

@@

\begin{document}

@@

\maketitle
\begin{abstract}

\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\input{chapters/1_introduction.tex}
\input{chapters/2_methods.tex}
\input{chapters/3_conclusions.tex}

>>>>

\documentclass{acm_proc_article-sp}

@@

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\begin{document}
\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, minimum width=6em]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]

@@

\maketitle
\begin{abstract}
The extensive growth of user-generated content in social networks and the common usage of emoticons and hashtags has introduced new possibilities to classify these information. In this paper, we provide an overview of the state-of-the-art regarding sentiment analysis of Twitter messages. The usefulness of existing lexical ressources and special expressions like smileys or hashtags is evaluated and an general introduction to sentiment analysis is provided as part of the introduction.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging}

\input{chapters/1_introduction.tex}
\input{chapters/4_preprocessing.tex}
\input{chapters/2_methods.tex}
\input{chapters/3_conclusions.tex}
